Composing Compilers

### 2021-10-26 prisc.tex
Remove \noindent
Get rid of a few hiccups

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PL'22]{ACM SIGPLAN Workshop on Principles of Secure Compilation}{January 22nd, 2022}{Philadelphia, PA, USA}
\acmYear{2022}
%\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%\startPage{1}

@@

  $$\uhcsitcomp{\bullet}=\lambda p.\begin{cases}\stcomp{p} &\text{if }p\in\src{\partials}\\
                                                \itcomp{p} &\text{if }p\in\irl{\partials}\end{cases}$$
\end{definition}
\noindent
We can derive a similar result to \Cref{lem:seqcompo} here, too:
\begin{lemma}[Upper Composition with RC]\label{lem:useqcompo}
  Given $\rtp{\stcomp{\bullet}}{\cC_{1}}$ and $\rtp{\itcomp{\bullet}}{\cC_{2}}$, then $\rtp{\uhcsitcomp{\bullet}}{\cC_{1}\cap\cC_{2}}$.
\end{lemma}
\Cref{lem:useqcompo} also generalises inductively to a number of compilers and classes.

@@

There exist several memory-safety instrumentations, both for target level~\cite{watson15,aurajo16,vassena19,kouwe17} and source level~\cite{nagarakatte10,akritidis09,rigger17,tarditi2018,sammler21}.
These compilation passes \textit{enforce} memory safety by adding static or dynamic checks to the program and, in the case of dynamic checks, crashing appropriately.
So, even though the programmer has written a memory-insecure program, we might still be interested in a memory-safe binary.

@@

\begin{definition}[Secure Instrumentation for Preserving $\cC$]\label{def:secure-instrumentation}
  A secure instrumentation with respect to some class $\cC$ enforces hyperproperties described by some class $\cC'$ without violating $\cC$-satisfying programs.
  We write $\sinstr{\stcomp{\bullet}}{\cC'}{\cC}$.
\end{definition}
Using this, we firstly want to inspect an insecure compilation chain from e.g.\ memory-safe $\src{Rust}$ to optimised, insecure $\irl{C}$, to memory-safe $\trg{CheckedC}$:
\begin{lemma}[Enforcement may preserve...]
  Given classes $\cC_{1},\cC_{2}$ and compilers $\sicomp{\bullet}$,$\itcomp{\bullet}$, we assume:

  \begin{itemize}
  \item $\rtp{\sicomp{\bullet}}{\cC_{1}}$
  \item $\sinstr{\itcomp{\bullet}}{\cC_{2}}{\cC_{1}}$
  \end{itemize}
\noindent
  Then, $\rtp{\sitcomp{\bullet}}{\cC_{1}\cup\cC_{2}}$.
\end{lemma}

Likewise, running a compiler that does not respect e.g.\ memory-safety after a memory-safety instrumentation nullifies the preservation of it:
\begin{lemma}[...but, order matters!]
  Given classes $\cC_{1},\cC_{2}$ and compilers $\sicomp{\bullet}$,$\itcomp{\bullet}$, we assume:

  \begin{itemize}
  \item $\sinstr{\sicomp{\bullet}}{\cC_{2}}{\cC_{1}}$
  \item $\rtp{\itcomp{\bullet}}{\cC_{1}}$
  \end{itemize}
\noindent
  Then, $\rtp{\sitcomp{\bullet}}{\cC_{1}}$.
\end{lemma}

We intend to study property-free characterisations of the presented material.
Another area is its specialisation to specific classes, such as $\cHSafety$, and subsets thereof.

>>>>

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PriSC'22]{ACM SIGPLAN Workshop on Principles of Secure Compilation}{January 22nd, 2022}{Philadelphia, PA, USA}
\acmYear{2022}
%\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%\startPage{1}

@@

  $$\uhcsitcomp{\bullet}=\lambda p.\begin{cases}\stcomp{p} &\text{if }p\in\src{\partials}\\
                                                \itcomp{p} &\text{if }p\in\irl{\partials}\end{cases}$$
\end{definition}
We can derive a similar result to \Cref{lem:seqcompo} here, too:
\begin{lemma}[Upper Composition with RC]\label{lem:useqcompo}
  Given $\rtp{\stcomp{\bullet}}{\cC_{1}}$ and $\rtp{\itcomp{\bullet}}{\cC_{2}}$, then $\rtp{\uhcsitcomp{\bullet}}{\cC_{1}\cap\cC_{2}}$.
\end{lemma}
\Cref{lem:useqcompo} also generalises inductively to a number of compilers and classes.

@@

To prevent such issues, a common approach for ensuring memory safety is to extend the source language~\cite{tarditi2018,sammler21}.
But, this is not always desirable, since source language extensions imply that existing programs might need a rewrite.
Instrumentation passes \textit{enforce} memory safety by adding dynamic checks to the program and crashing appropriately, thus leaving the features of the source language untouched.
There exist several memory-safety instrumentations, both for target level~\cite{watson15,aurajo16,vassena19,kouwe17} and source level~\cite{nagarakatte10,akritidis09,rigger17}.
So, even though the programmer has written a memory-insecure program, we might still be interested in a memory-safe binary.

@@

\begin{definition}[Secure Instrumentation for Preserving $\cC$]\label{def:secure-instrumentation}
  A secure instrumentation with respect to some class $\cC$ enforces hyperproperties described by some class $\cC'$ without violating $\cC$-satisfying programs.
  We write $\sinstr{\stcomp{\bullet}}{\cC'}{\cC}$.
\end{definition}
Using this, we firstly want to inspect an insecure compilation chain from e.g.\ memory-safe $\src{Rust}$ to optimised, insecure $\irl{C}$, to memory-safe $\trg{CheckedC}$:
\begin{example}[Enforcement may preserve...]
  Given classes $\cC_{1},\cC_{2}$ and compilers $\sicomp{\bullet}$,$\itcomp{\bullet}$, we assume:

  \begin{itemize}
  \item $\rtp{\sicomp{\bullet}}{\cC_{1}}$
  \item $\sinstr{\itcomp{\bullet}}{\cC_{2}}{\cC_{1}}$
  \end{itemize}
\noindent
  Then, $\rtp{\sitcomp{\bullet}}{\cC_{1}\cup\cC_{2}}$.
\end{example}

Likewise, running a compiler that does not respect e.g.\ memory-safety after a memory-safety instrumentation nullifies the preservation of it:
\begin{example}[...but, order matters!]
  Given classes $\cC_{1},\cC_{2}$ and compilers $\sicomp{\bullet}$,$\itcomp{\bullet}$, we assume:

  \begin{itemize}
  \item $\sinstr{\sicomp{\bullet}}{\cC_{2}}{\cC_{1}}$
  \item $\rtp{\itcomp{\bullet}}{\cC_{1}}$
  \end{itemize}
\noindent
  Then, $\rtp{\sitcomp{\bullet}}{\cC_{1}}$.
\end{example}

We also intend to study property-free characterisations of the presented material.
Another area is its specialisation to specific classes, such as $\cHSafety$, and subsets thereof.
